Discrete Quantum Theories and Computing

### 2019-01-29 dissertation.tex
dissertation.lyx Acknowledgments Updating...

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{italian}
\setotherlanguage{turkish}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

and~\ref{chap:DQT=000026DQC} is based on \cite{geometry2013} and \cite{DQT2014}; most of Chapter~\ref{chap:QIVPM} is
based on \cite{THOS2018}.\tabularnewline\addlinespace

@@

 &  & Suggested &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop

@@

and \cite{doi:10.1142/S0217984913500644},

@@

me as a committee members, and taught me which become the bases or
inspired any part of my dissertation as listed in Table~\ref{tab:acknowledgments}.
Especially, Prof.\ Gerardo Ortiz, Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري}),
and Prof.\ Andrew J. Hanson meet me weekly for the pass few years,
read and tried to understand what I typed which sometimes even myself
cannot understand, taught me how to organize them in ``English''
so that general audience might be interested and have some chance
to understand, and encourage me to participate seminars, workshops,
and conferences. Prof.\ Lawrence Moss invited me to present our results
in the interdisciplinary logic seminar and theory seminar in Computer
Science and wrote an assessment letter for me. Although not directly
related to this dissertation, the knot theory studied with Prof.\ Dylan
Paul Thurston and the quantum interpretation discussed with Prof.\ Shouhong
Wang (汪守宏) also broadened my understanding on quantum theory and computing.
I would like express my appreciation to all of these.

Besides of Table~\ref{tab:acknowledgments}, I have some inspiring
discussion with John Gardiner about quantum probability measures over
finite fields~\cite{Gardiner2014}, and his results are improved
and motivated the transition from DQT to QIVPM in Sec.~\ref{sec:Toward-IVPM}.
Also, some unpublished computation for deterministic quantum algorithms
is organized in the term paper for SLST-T501 Academic Writing course.
I want to thank Prof.\ Tom Lewis for proof-reading them, and they
become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on expressing myself in English as well.
Others who help me indirectly on the content of dissertation including
Kin Wai Chan, Prof.\ 朱樺, Weihua Liu (刘伟华), 劉鈺平, Meng-Wei Chen
(陳孟瑋), \ldots , etc. This could be listed on and on, and I still
thank you even if your name is not listed here.\todo{Acknowledgments
cleaned up until here. }

>>>>

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{german}
\setotherlanguage{italian}
\setotherlanguage{turkish}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

and~\ref{chap:DQT=000026DQC} is based on~\cite{geometry2013} and~\cite{DQT2014}; most of Chapter~\ref{chap:QIVPM} is
based on~\cite{THOS2018}.\tabularnewline\addlinespace

@@

 &  & Supervisor &  &  &  &  & The application for Rethinking Foundations of Physics 2017 workshop

@@

and~\cite{doi:10.1142/S0217984913500644},

@@

me as a committee members, and taught me so that our work or studies
became the bases or inspired any part of my dissertation as listed
in Table~\ref{tab:acknowledgments}. Especially, Prof.\ Andrew J.
Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})
meet me weekly for the pass few years, read and tried to understand
what I typed which sometimes even myself cannot understand, taught
me how to organize them in ``English'' so that general audience
might be interested and have some chance to understand, and encouraged
me to participate seminars, workshops, and conferences. Prof.\ Lawrence
Moss invited me to present our results in the interdisciplinary logic
seminar and theory seminar in Computer Science and wrote an assessment
letter for me. Although not directly related to this dissertation,
the \textgerman[variant=german,spelling=new,babelshorthands=true]{Weil}
conjecture on Grassmannians studied with Prof.\ Dylan Paul Thurston
and the quantum interpretation discussed with Prof.\ Shouhong Wang
(汪守宏) also broadened my understanding on discrete and conventional
quantum theories. I would like express my appreciation to all of these.

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Also, the unpublished computation
for the discrete Deutsch algorithm \cite{Deutsch1985,544199,Mermin2007}
is organized in the term paper for SLST-T501 Academic Writing course.
I want to thank Prof.\ Tom Lewis for proof-reading them, and they
become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on how to communicate in English as well.
Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Prof.\ Huah Chu (朱樺), Weihua Liu (刘伟华), Caren Liu
(劉鈺平), Meng-Wei Chen (陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen
(陳昭宏)\ldots , etc. This could be listed on and on. I still thank
you even if your name is not listed here, and sorry for my bad memory.\todo{Acknowledgments
cleaned up until here. }
